Estimating duration using survival analysis

### 2024-08-02 cis-perfect-testing.tex
clarify nest stuff

A related problem is estimating how long insect and bird nests survive for
In this context detected events are doubly interval censored and some events are undetected; Bayesian methods have been developed which augment the data with the unobserved times of infection~\autocite{heBayesiana,heBayesian,caoModeling}.
The data augmentation approach creates a parameter for each detected infection.
This increases the dimensionality of the problem greatly, making it computationally infeasible with the large sample size of the CIS within the SRS.

>>>>

Bayesian methods have been used for nest survival before~\autocite{heBayesiana,heBayesian,caoModeling} by augmenting the data with the unobserved times.
The data augmentation approach creates a parameter for each detected infection.
This increases the dimensionality of the problem greatly, making it computationally infeasible with the large sample size of the CIS within the SRS.
